\NAME: A framework for \\ Efficient Intrusion Detection\\ in the Internet of Things

### 2014-10-28 paper.tex
added draft conclusion

\TODO

theoretical gains are met in practice

explore more domains + implement corresponding DSLs for embedded systems

extract generic language as host for DSLs

Integration of applications with generated IDS allows actively and dynamically
responding to changes in the reputation of other nodes.

The services running on those devices can take advantage of these local
security layers. If the IDS detects a problem, the service can immediately
terminate the communication with the attacker, before it's actually abused.

>>>>

Wireless resource constraint devices require that software respects their
energy restrictions. Efficiently adding multiple intrusion detection algorithm
requires fusion of these algorithms on a functional level, to reduce execution
inefficiencies, redundant memory usage and superfluous network access.

In this paper we introduced \NAME, a framework consisting of a DSL, a source
code generator and accompanying software library. Using the DSL, intrusion
detection algorithms can be formally described in such way that, using
functional code fusion during source code generation, it is possible to
interpret their functional meaning and merge common functionality and shared
data. The software library hosts common functionality, such as network message
parsing, sent message aggregation, event scheduling,\dots as a framework for
the generator to apply.

Initial experiments confirm the theoretical positive impact on the use of
resources. The platform independent DSL enables generation of source code
targeting different platforms and languages, which allows high degrees of reuse
in heterogenous environments and different configurations.

Near future research will focus on the integration of applications with the
generated intrusion detection systems. We see opportunities to allow
application to actively and dynamically respond to intrusions as they are
detected and avoid malicious payload to harm them.

A continued effort is targeting the reduction of non-platform independent parts
in the implementation. This way it is possible to add more platforms and
languages with less effort.

In the longer run, we want to investigate the possibility to extend the
functional code fusion paradigm to other domains beyond intrusion detection.
